---
title: "What Makes us Happy?"
author: "Yuki Ogawa"
date: "2022-11-18"
output: pdf_document
---

## About Dataset
World Happiness Report

 - source: https://www.kaggle.com/datasets/unsdsn/world-happiness
 - year: 2019
 - 156 countries

## Terms Used in Dataset

 - **GDP per capita**:GDP per capita is a measure of a country's economic output that accounts for its number of people.
 - **Social support**:Social support means having friends and other people, including family, to turn to in times of need or crisis to give you a broader focus and positive self-image. Social support enhances quality of life and provides a buffer against adverse life events.
 - **Healthy life expectancy**:Healthy Life Expectancy is the average number of years that a newborn can expect to live in "full health"—in other words, not hampered by disabling illnesses or injuries.
Freedom to make life choices:Freedom of choice describes an individual's opportunity and autonomy to perform an action selected from at least two available options, unconstrained by external parties.
 - **Generosity**:the quality of being kind and generous.
 - **Perceptions of corruption**:The Corruption Perceptions Index (CPI) is an index published annually by Transparency International since 1995 which ranks countries "by their perceived levels of public sector corruption, as determined by expert assessments and opinion surveys.

## What Makes us Happy? 
In recent years, there has been much sad news, including a coronavirus pandemic and a prolonged war in Ukraine.
The fast-changing news make us pessimistic. Thus, I want to know what makes us happy, and have a great time. 

\newpage

## Library and Loading Data

```{r warning=FALSE}
library(ggplot2)
library(reshape2)
library(dplyr)
library(maps)
library(countrycode)
df_2019 <- read.csv("dataframes/2019.csv")
```

\newpage

## Correlation heatmap

Happiness Score is a target.
The heatmap shows that GDP per capita, Social Support, and Health are correlated with Happiness Score.

```{r}
ggcorrplot::ggcorrplot(cor(df_2019[,3:9], method="pearson"))
```
\newpage

## The top 10 countries

This bar plot also shows that GDP per capita, Social Support, and Health are major factors.

These three elements consist of 70% of total approximately.

"Social Support" seems the biggest proportion in the most top-10 countries.

Is this a worldwide trend?

```{r}
melted_df_2019 <- df_2019 %>%
  select("Country.or.region", "GDP.per.capita", "Social.support", "Healthy.life.expectancy","Freedom.to.make.life.choices","Generosity",
         "Perceptions.of.corruption") %>% head(10) %>% melt()
ggplot(data=melted_df_2019, aes(x=Country.or.region, y=value, fill=variable))+
  geom_bar(stat="identity")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  labs(x="Country")
```

\newpage

## Which is the strongest in each country? 

The map below shows that Social Support is highest in most countries. 

(GDP per caipta is highest in Middle east.) 

Why is Social support highest in most countries? Is this data set skewed?

```{r results='hide', warning=FALSE}
highest_element <- colnames(df_2019[,4:9])[max.col(df_2019[,4:9])]
df_2019_1 <- cbind(df_2019, highest_element)

df_2019_1 <- df_2019_1 %>% 
  mutate(iso3c = countrycode(sourcevar = Country.or.region,
                             origin = "country.name", destination = "iso3c"))
df_2019_1 %>%
  filter(is.na(iso3c) == TRUE) %>%
  select(Country.or.region) %>%
  distinct()

world <- map_data("world")
world <- world %>% 
  mutate(iso3c = countrycode(sourcevar = region,
                             origin = "country.name", destination = "iso3c"))
world %>%
  filter(is.na(iso3c) == TRUE) %>%
  select(region) %>%
  distinct()

left_join(world, df_2019_1, by = "iso3c") %>% 
  ggplot() + 
  geom_polygon(aes(x = long, y = lat, group = group, fill = highest_element),
               colour = "black", size = 0.1)+
  labs(fill="Highest Element")
```

\newpage

# Histogram of Social Support
The mean line is red. 

This histogram is unimodal, with the peak located to the right.

Thus, social support is likely to be high in many countries.

Let me compare it with other two elements (GDP per capita and Health).

```{r}
hist(df_2019$Social.support,
     breaks=seq(min(df_2019$Social.support), max(df_2019$Social.support),
                length.out = 20),
     xlab = "Social Support",
     main="Histogram of Social Support",
     col = "blue")
par(new=T)
abline(v=mean(df_2019_1$Social.support), col='red', lwd=3)
```

\newpage

# Box Plot of Top 3 Factors 

Social support is likely to be higher than other two elements.

This plots explains why the previous map is filled in blue (social support).

GDP per capita (the middle plot) has a wide interquartile range.

```{r}
boxplot(df_2019$Social.support, df_2019$GDP.per.capita,df_2019$Healthy.life.expectancy,
        horizontal = T,
        names = c("Social Support", "GDP per capital", "Health"),
        col=c('blue', 'pink', 'green'))
```

## Answer

Happiness was found to be related to multiple factors: GDP per capita, Social Support, and Health.

This survey was conducted on a national basis and not on an individual basis. To begin with, the feeling of happiness is a subjective thing that varies from person to person. In order to capture happiness objectively, each factor is scored. The data indicate that the three factors of GDP per capita, social support, and health are particularly important. Translated to individuals, their own productivity (earning), relationships with family and friends, and health are important. We can lead a fulfilling life by being aware of these factors.

\newpage 

Finally, I analyze what my home country, Japan, needs to do to raise its happiness score. As the below row shows, Japan's rank is 58. The score is almost 2 points lower than the first-place, Finland.

```{r}
df_2019[58,1:3]
df_2019[1,1:3]
```

## Healthy.life.expectancy Ranking

Japan is the third. 
```{r}
head(df_2019[order(df_2019$Healthy.life.expectancy,decreasing = TRUE),2:6]) %>%
  select(Country.or.region, Healthy.life.expectancy)
```

\newpage

## Japan and Top 10 Countries 

The bar plots below shows the proportion of each element by country. 

The proportion of Health in Japan is large because Japan is one of the most high average life expectancy countries.

The other proportion of Japan is similar to other countries. Japan scores low overall. 
```{r}

melted_japan <- df_2019[58,] %>%
  select("Country.or.region", "GDP.per.capita", "Social.support", "Healthy.life.expectancy","Freedom.to.make.life.choices","Generosity", "Perceptions.of.corruption")  %>% melt()
melted_japan <- rbind(melted_japan, melted_df_2019)

ggplot(data=melted_japan, aes(x=Country.or.region, y=value, fill=variable))+
  geom_bar(stat="identity", position="fill")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  labs(x="Country", )
```
